Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations. Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications. Secondly, in the sequential data regime data arrives not in batches

@@

%% CL section 
%%
%% EWC, SI, VCL -> weight regularization 
% 1) what is the central problem of CL? 
% 		Training from a non-stationary distribution the models overwrites the previously learnt parameters and then forgets the previous learnt function.
% 2) What others have done?
% 		starting with EWC and SI, that are the most known methods in term of weight regularization. And others took a different approach again in the weight regularization real with VCL (to check)
% 3) People started to try experimenting with the functional regularization -> 
% In order of complexity -> DER, FROMP, S-FSVI
% In order of pubblication -> DER/FROMP, K-Priors (?), S-FSVI
EWC \cite{kirkpatrick2017overcoming}
SI \cite{zenke17a}, 
VCL \cite{nguyen-tuongModel2009},

@@

\section{Methods}
\label{sec:methods}
%
In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where the regularization weight takes the role of a prior precision parameter, \ie, $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$.

@@

- distribution over w given to you by the non-linear function. One could sample over weights pass it over the function and you have distribution over functions. HMC is heavy, structure of the problem around the map estimate. characteruze this as the first two moments of the distributions over the functions restrict to the first two moments.

Replace with a taylor series at the MAP first order taylor expansion in w. degenerate cov function.

- more citations there.

- GP induced by the trained neural network. not GP prior.

- Add the NTK bit back in.

- assume that when you are at the map estimate when you have converged this should be small.

- Write out that w beomces zero under the expectation.

-  transition from background to methods.

- More explination of the dual equation 5 the loss landscape link. Perbutation point linked directly to that here.

-

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning with image data. SVGP is our method, and the number inside parentheses is the number of inducing points. SVGP NN is a modification of our method, where the mean is from the NN directly and the variance is from the GP model} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{6pt}
	\setlength{\tblw}{0.2\textwidth}

>>>>

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations. Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications. Secondly, in the sequential data regime.

@@

%% CL section 
%%
%% EWC, SI, VCL -> weight regularization

EWC \cite{kirkpatrick2017overcoming}
SI \cite{zenke17a}, 
VCL \cite{nguyen-tuongModel2009},

@@

\section{Methods}
\label{sec:methods}
%
In supervised learning, given a data set $\dataset = \{(\mathbf{x}_{i} , \mathbf{y}_{i})\}_{i=1}^{n}$, with input $\mathbf{x}_i \in \inputDomain$ and output $\mathbf{y}_i \in \outputDomain$ pairs, the weights $\weights \in \R^{P}$ of a neural network, $f_\mathbf{w} : \inputDomain \to \outputDomain$, are usually trained to minimize the (regularized) empirical risk,
%
\begin{equation} \label{eq-empirical-risk}
  \weights^{*} = 
  \arg \min_{\weights} \mathcal{L}(\dataset,\weights) =
  \arg \min_{\weights} \sum_{i=1}^{n} \ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) + \delta \mathcal{R}(\weights).
\end{equation}
%
If $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i) = -\log(p(\mathbf{y} \mid f_\weights(\mathbf{x}_{i}))$ and the regularizer $\mathcal{R}(\weights) = \frac{1}{2}\|\weights\|^{2}_2$, then we can view \cref{eq-empirical-risk} as the maximum {\it a~posteriori} (MAP) solution to a Bayesian objective, where $p(\vw) = \Norm(\vzeros, \delta^{-1} \MI)$, where the regularization weight takes the role of a prior precision parameter.

@@

@@

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Metrics for supervised learning with image data} 
	\label{tbl:imagesuper}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{6pt}
	\setlength{\tblw}{0.2\textwidth}
